---
title: "Single Data Operations"
author: "R package build"
date: '2022-02-14'
slug: single-data-operations
categories: []
tags: []
---

# Hotel Bookings 
```{r}
library(tidyverse)
```
```{r}
url <- 'https://github.com/nataliesouza/tidyverse/blob/main/hotels.csv?raw=true'
hotels <- read_csv(url)
names(hotels)
```

# Select Commands
```{r}
hotels %>%
  select(hotel, lead_time)
```
```{r}
hotels %>%
  select(-agent)
```
```{r}
hotels %>%
  select(hotel:arrival_date_month)
```
```{r}
hotels %>%
  select(starts_with("arrival"))
```
```{r}
hotels %>%
  select(ends_with("type"))
```
# Select and Arrange Command
```{r}
hotels %>%
  select(adults, children, babies) %>%
  arrange(desc(babies))
```

# Slice Command (first five rows)
```{r}
hotels %>%
  slice(1:5)
```
# Filter Commands

## Filter a subset of rows 
```{r}
hotels %>%
  filter(hotel == "City Hotel")
```

## Filter for many conditions 
```{r}
hotels %>%
  filter( 
    adults == 0,
    children >= 1
    ) %>% 
  select(adults, babies, children)
```
## Filter Complex Conditions 
```{r}
hotels %>%
  filter( 
    adults == 0,     
    children >= 1 | babies >= 1     # | means or
    ) %>%
  select(adults, babies, children)
```
# Distinct Command 
## To filter for unique rows
```{r}
hotels %>% 
  distinct(hotel, market_segment) %>%
  arrange(hotel, market_segment)
```
# Count Command
## To create frequency tables (alphabetical)
```{r}
hotels %>%
  count(market_segment)
```
## To create multiple variables (attention to order!)
```{r}
hotels %>%
  count(hotel, market_segment)
```
```{r}
hotels %>%
  count(market_segment, hotel)
```

## To create frequency tables (descending)
```{r}
hotels %>%
  count(market_segment, sort = TRUE)
```
# Count and Arrange Command 
```{r}
hotels %>%
  count(market_segment) %>%
  arrange(desc(n))
```

# Mutate Command 
## Adding new variable
```{r}
hotels %>%
  mutate(little_ones = children + babies) %>%
  select(children, babies, little_ones) %>%
  arrange(desc(little_ones))
```
## Resort Hotel
```{r}
hotels %>%
  mutate(little_ones = children + babies) %>%
  filter(
    little_ones >= 1,
    hotel == "Resort Hotel"
    ) %>%
  select(hotel, little_ones)
```
## City Hotel
```{r}
hotels %>%
  mutate(little_ones = children + babies) %>%
  filter(
    little_ones >= 1,
    hotel == "City Hotel"
    )  %>%
  select(hotel, little_ones)
```
# Summarize Command 
## Summary Statistics 
### Mean average daily rate for all books
```{r}
hotels %>%
  summarise(mean_adr = mean(adr))
```
### Stats
```{r}
hotels %>%
  summarise(
    min_adr = min(adr),
    mean_adr = mean(adr),
    median_adr = median(adr),
    max_adr = max(adr)
    )
```

# Group Command
## Grouped operations 
### Mean average daily rate for all booking at city and resort hotels
```{r}
hotels %>%
  group_by(hotel) %>%
  summarise(mean_adr = mean(adr))
```
# Two possible ways of calculating frequencies 
## Group_by
```{r}
hotels %>%
  group_by(hotel) %>%
  summarise(n = n())
```
## Count
```{r}
hotels %>%
  count(hotel)
```





