---
title: "Data Types"
author: "R package build"
date: '2022-02-21'
slug: data-types
categories: []
tags: []
---
# Call library
```{r}
library(tidyverse)
```

# Upload Url
```{r}
url <- 'https://raw.githubusercontent.com/nataliesouza/tidyverse/main/cat-lovers.csv'
cat_lovers <- read_csv(url)
names(cat_lovers)
```

#Summarizing Cat Lovers Data Set
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats))
```
```{r}
?mean
```
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```

```{r}
glimpse(cat_lovers)
```
# Fixing the bad data in the numeric column 
```{r}
cat_lovers %>%
  mutate(number_of_cats = case_when(
    name == "Ginger Clark" ~ 2,
    name == "Doug Bass"    ~ 3,
    TRUE                   ~ as.numeric(number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))
```
# Numeric Data Summarization
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))
```

```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```

# Data Types (Logical, character, double, and integer)
```{r}
typeof(TRUE)
typeof("hello")
typeof(1.3335)
typeof(7)
typeof(7L)
typeof(1:3)
```
#Concatenation
```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))
```

# Explicit Coercion
Number vs. character 
```{r}
x <- 1:3
x
typeof(x)
typeof(as.character(x))
```
```{r}
y <- as.character(x)
y
typeof(y)
```
Number vs. Logical 
```{r}
x <- c(TRUE, FALSE)
x
typeof(x)
typeof(as.numeric(x))
```
```{r}
y <- as.numeric(x)
y
typeof(y)
```
#Implicit Coercion 
```{r}
c(1, "Hello")
c(FALSE, 3L)
c(1.2, 3L)
c(2L, "two")
```

# Exercise 
## Suppose we want to know the type of c(1, "a"). First, I'd look at:
```{r}
typeof(1)
typeof("a")
typeof(c(1, "a"))
```
# Special Values
## +/- Infinity and Not a Number
```{r}
pi/0
0/0
1/0 - 1/0
1/0 + 1/0
```
## Not Available "NA"
```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)
mean(x, na.rm = TRUE)
summary(x)
typeof(NA)
```
# Mental model for NAs
```{r}
TRUE | NA
FALSE | NA
TRUE | TRUE
TRUE | FALSE
FALSE | TRUE
FALSE | FALSE
```







