---
title: "Importing Data"
author: "R package build"
date: '2022-02-23'
slug: importing-data
categories: []
tags: []
---

# Call Libraries
```{r}
library(tidyverse)
library(readr)
library(readxl)
library(dplyr)
```

# Information on Readr 
## read_csv() - comma delimited files
## read_csv2() - semicolon separated files (common in countries where , is used as the decimal place)
## read_tsv() - tab delimited files
## read_delim() - reads in files with any delimiter
## read_fwf() - fixed width files

# Information on Readxl
## read_excel() - read xls or xlsx files

# Reading Data
```{r}
nobel <- read_csv(file = "https://raw.githubusercontent.com/dearbharat/tidyverse/main/nobel.csv")
nobel
df <- read_csv(file = "https://raw.githubusercontent.com/dearbharat/tidyverse/main/df.csv")
df
```

# Writing Data
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "df.csv")
```

# Variable Names 
```{r}
edibnb_badnames <- read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/edibnb-badnames.csv")
names(edibnb_badnames)
```

## Defining Column Names
```{r}
edibnb_col_names <- read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/edibnb-badnames.csv",
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)
```

## Formating text to snake_case
```{r}
edibnb_clean_names <- read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/edibnb-badnames.csv") %>%
  janitor::clean_names()
names(edibnb_clean_names)
```

# Variable Types
```{r}
read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/df-na.csv")
```

## Explicit NAs
```{r}
read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/df-na.csv", 
         na = c("", "NA", ".", "9999", "Not applicable"))
```

## Specify Column Types 
```{r}
read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/df-na.csv", col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```

# Case Study: Favorite Foods 
# Favorite Foods
```{r}
fav_food <- read_excel("favourite-food.xlsx")
fav_food
```

## Variable Names 
```{r}
fav_food <- read_excel("favourite-food.xlsx") %>%
  janitor::clean_names()
fav_food
```

## Handling NAs
```{r}
fav_food <- read_excel("favourite-food.xlsx",
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```

## Making age numeric
```{r}
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```

## Socio-economic status 
What order are the levels of ses listed in?
```{r}
fav_food %>%
  count(ses)
```

## Make Socio-economic status a factor
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```

# Final Result after putting everything together 
```{r}
fav_food <- read_excel("favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```

# Writing and Reading Files
```{r}
write_csv(fav_food, file = "fav-food-clean.csv")
fav_food_clean <- read_csv("https://raw.githubusercontent.com/dearbharat/tidyverse/main/fav-food-clean.csv")
```

## Checking Socio-economic status
```{r}
fav_food_clean %>%
  count(ses)
```

