---
title: 'A03: Logistic Regression on Titanic Dataset'
author: R package build
date: '2022-03-31'
slug: a03-logistic-regression-on-titanic-dataset
categories: []
tags: []
---
## Call library
```{r}
library(titanic)
library(readr)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(RColorBrewer)
library(broom)
library(tidyverse)
library(rpart)
```

## Load datasets
```{r}
test_data <- read_csv("https://raw.githubusercontent.com/nataliesouza/website/master/test.csv")
titanic_test$Survived <- NA
head(test_data)

train_data <- read_csv("https://raw.githubusercontent.com/nataliesouza/website/master/train.csv")
head(train_data)
```
## Cleaning Data Set
```{r}
nrow(train_data)
sum(is.na(train_data))
colSums(is.na(train_data))
str(train_data)
train <- train_data[, -(names(train_data) == "PassengerId")] #has no value to the expected model
train_data <- na.omit(train_data)
```
## Missing Data From test_data
```{r}
nrow(test_data)
sum(is.na(test_data))
colSums(is.na(test_data))
str(test_data)
```
## Checking for Survival Patterns in train_data
```{r}
table(train_data$Survived, train_data$Pclass)
table(train_data$Survived, train_data$Sex) #seems to be related
table(train_data$Survived, train_data$Age)
table(train_data$Survived, train_data$SibSp)
table(train_data$Survived, train_data$Parch) #seems to be related
table(train_data$Survived, train_data$Fare) #seems to be related
table(train_data$Survived, train_data$Embarked)
```
## Checking the Distribution 
```{r}
fare0 <- hist(train_data[train_data$Survived == "0",]$Fare)
fare1 <- hist(train_data[train_data$Survived == "1",]$Fare)

parch0 <- hist(train_data[train_data$Survived == "0",]$Parch)
parch1 <- hist(train_data[train_data$Survived == "1",]$Parch)
```


## Checking for Patterns in Gender
```{r}
women <- subset(train_data, train_data$Sex=="female")
count(women)
number_of_women <- count(women)

survived_women <- subset(women, women$Survived==1)
count(survived_women)
number_of_survived_women <- count(survived_women)

rate_women <- number_of_survived_women/number_of_women
rate_women
```
```{r}
men <- subset(train_data, train_data$Sex=="male")
count(men)
number_of_men <- count(men)

survived_men <- subset(men, men$Survived==1)
count(survived_men)
number_of_survived_men <- count(survived_men)

rate_men <- number_of_survived_men/number_of_men
rate_men
```
## Visualization of the Data (male and female who died and survived)
```{r}
table(train_data$Sex, train_data$Survived)
```
```{r}
prop.table(table(train_data$Sex, train_data$Survived), margin = 1)
```

## Plot showing the majority of passengers who survived
```{r}
df <- ggplot(train_data, aes(Survived))
df + geom_bar(aes(fill = Sex), width=0.85, colour="red") + scale_fill_brewer() +
  ylab("Survival Count By Gender") +
  xlab("Survived: No = 0, Yes = 1") +
  ggtitle("Gender Vs. Survival (train_data)")
```

## Random Forest Model
```{r}
library(randomForest)
train_data$Survived <- as.factor(train_data$Survived)
rf <- randomForest(
  Survived ~ .,
  data = train_data
)

rf #this is based on the removed missing values
```

##Converting the rest of the variables into factors
```{r}
test_data$Sex <- as.factor(test_data$Sex)
test_data$Embarked <- as.factor(test_data$Embarked)
test_data$Parch <- as.factor(test_data$Parch)
test_data$Fare <- as.factor(test_data$Fare)

train_data$Sex <- as.factor(train_data$Sex)
train_data$Embarked <- as.factor(train_data$Embarked)
test_data$Parch <- as.factor(test_data$Parch)
test_data$Fare <- as.factor(test_data$Fare)
sapply(train_data, class)
```

```{r}
importance(rf)
create_rfplot <- function(rf, type){
  imp <- importance(rf, type = type, scale = F)
  featureImportance <- data.frame(Feature = row.names(imp), Importance = imp[, 1])
  p <- ggplot(featureImportance, aes(x = reorder(Feature, Importance), y = Importance)) +
  geom_bar(stat = "identity", fill = "#53cfff", width = 0.65) +
  coord_flip() +
  theme_light(base_size = 20) +
  theme(axis.title.x = element_text(size = 15, color = "black"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_text(size = 15, color = "black"))
  return(p)
} # I saw a similar function in a website and I thought it would work well with the titanic data, so I just adjusted it to my variables
create_rfplot(rf, type = 2)
```
# Logistic Regression 
```{r}
test_data <- read_csv("https://raw.githubusercontent.com/nataliesouza/website/master/test.csv")
train_data <- read_csv("https://raw.githubusercontent.com/nataliesouza/website/master/train.csv")
test_data$Survived <- NA
complete_data <- rbind(train_data, test_data)
str(complete_data)
```

## Analyzing Complete Data df
```{r}
colSums(is.na(complete_data))
complete_data$Embarked[complete_data$Embarked==""] <- "S"
complete_data$Age[is.na(complete_data$Age)] <- median(complete_data$Age,na.rm=T)
```

## Cleaning up Complete Data df
```{r}
titanic_data <- complete_data %>% select(-c(Cabin, PassengerId, Ticket, Name))
titanic_data$Survived <- as.factor(titanic_data$Survived)
titanic_data$Sex <- as.factor(titanic_data$Sex)
titanic_data$Pclass <- as.factor(titanic_data$Pclass)
titanic_data$Embarked <- as.factor(titanic_data$Embarked)
```

## Setting Seed 
```{r}
set.seed(222)
t = sample(1:nrow(titanic_data), 0.7*nrow(titanic_data))
train = titanic_data[t,]
test = titanic_data[-t,]
```
## Creating model
```{r}
library(car)
library(car)
model <- lm(Survived~., data=train)
t = vif(model)
sort(t, decreasing=TRUE)
model1<- glm(as.factor(Survived)~., family="binomial", data=train)
summary(model1)
```
## Discarding Parch and Embarked Variables
```{r}
stepmodel = step(model1, direction = "both")
formula(stepmodel)
summary(stepmodel)
```

## Predicting Score of "train"
```{r}
train$score <- predict(stepmodel, newdata = train, type="response")
head(train$score)
```
```{r}
tail(train$score)
```

## Final Model and Predictions
```{r}
train$prediction <- ifelse(train$score>=0.6, 1, 0)
table(factor(train$prediction), factor(train$Survived))
```
### The model indicates an accuracy of 80.06% -> 502/627 = 0.8006 in regards to the train data-set

```{r}
test$score<-predict(stepmodel, test, type = "response")
head(test$score)
```
```{r}
test$predicted<-ifelse(test$score>=0.6, 1, 0)
head(test$predicted)
```
```{r}
table(factor(test$predicted), factor(test$Survived))
```

### The model indicates an accuracy of 81.68% -> 214/262 = 0.8168 in regards to the test data-set 

### Comments: I tried using the cheat sheet for Python datadrame to R dataframe, from what I was able to find online for this titanic data-set from kaggle's tutorials. 


