---
title: "A02:Regression Models"
author: "R package build"
date: '2022-03-26'
slug: a02-regression-models
categories: []
tags: []
---
# Call libraries
```{r}
pacman::p_load(pacman, magrittr, productplots, psych, RColorBrewer, tidyverse)
library(tidyr)
```

# Import data from gitHub
```{r}
library(readxl)
data <- read_excel("~/Documents/DataScience/website/resources/_gen/assets/Professor_Proposes_Data.xlsx")
summary(data)
sum(is.na(data))
```

# Univariate Analysis 
```{r}
## Summary Statistics (Price)
summary(data$Price)
```

```{r}
## Histogram and Density Plot (Price)
hist(data$Price)
plot(density(data$Price))
```
```{r}
## Summary Statistics (Carat)
summary(data$Carat)
```

```{r}
## Histogram and Density Plot (Carat)
hist(data$Carat)
plot(density(data$Carat))
```
```{r}
## Counting number of records (Clarity)
table(data$Clarity)
```

```{r}
## Frequencies (Clarity)
library(summarytools)
summarytools::freq(data$Clarity, order = "freq")
```


```{r}
## Counting number of records (Color)
table(data$Colour)
```


```{r}
## Frequencies (Color)
library(summarytools)
summarytools::freq(data$Colour, order = "freq")
```
```{r}
## Counting number of records (Cut)
table(data$Cut)
```

```{r}
## Frequencies (Cut)
library(summarytools)
summarytools::freq(data$Cut, order = "freq")
```

```{r}
## Counting number of records (Certification)
table(data$Certification)
```

```{r}
## Frequencies (Certification)
library(summarytools)
summarytools::freq(data$Certification, order = "freq")
```
```{r}
## Counting number of records (Polish)
table(data$Polish)
```

```{r}
## Frequencies (Polish)
library(summarytools)
summarytools::freq(data$Polish, order = "freq")
```

```{r}
## Counting number of records (Symmetry)
table(data$Symmetry)
```

```{r}
## Frequencies (Symmetry)
library(summarytools)
summarytools::freq(data$Symmetry, order = "freq")
```

# Bivariate Analysis of Metric Data
```{r}
library(tidyverse)
ggplot(data, aes(Carat, Price)) + 
    geom_point()
```
# Focus on High Carat High Price Data Set
```{r}
ggplot(data, aes(Carat, Price)) + 
    geom_point() +
    coord_cartesian(xlim = c(0.7, 1.7), ylim = c(1800, 3250))
```
# Focus on Low Carat Price Low Price Data Set
```{r}
ggplot(data, aes(Carat, Price)) + 
    geom_point() +
    coord_cartesian(xlim = c(0.0, 0.4), ylim = c(0.0, 1000))
```

# Regression Analysis with Carat
```{r}
library(ggplot2)
carat.lm <- lm(Price ~ Carat, data = data)
summary(carat.lm)
```
## Comments: for some reason my results were not equivalent to the ones present in the Solution document.

# Regression analysis with Clarity
```{r}
clarity.lm <- lm(Price ~ Clarity, data = data)
summary(clarity.lm)
```
## Comments: results are closer to the ones present in Solution documents.

# Bivariate Analysis of Non-metric data
```{r}
color.lm <- lm(Price ~ Colour, data = data)
summary(color.lm)
```

```{r}
cut.lm <- lm(Price ~ Cut, data = data)
summary(cut.lm)
```

```{r}
certification.lm <- lm(Price ~ Certification, data = data)
summary(certification.lm)
```

```{r}
polish.lm <- lm(Price ~ Polish, data = data)
summary(polish.lm)
```

```{r}
symmetry.lm <- lm(Price ~ Symmetry, data = data)
summary(symmetry.lm)
```

# Multiple Regression 
```{r}
price.lm <- lm(Price ~ Cut + Colour + Clarity + Certification + Polish + Carat, data = data)
summary(price.lm)
```

```{r}
par(mfrow = c(2,2))
plot(price.lm)
par(mfrow = c(1,1))
```

# Bootstrap resampling 
```{r}
library(tidyverse)
library(broom)
```
## Low Price Data Set
```{r}
nlsfit <- nls(Price ~ k / Carat + b, data, start = list(k = 1, b = 0))
ggplot(data, aes(Carat, Price)) +
    geom_point() +
    coord_cartesian(xlim = c(0.7, 1.7), ylim = c(1800, 3250)) +
    geom_line(aes(y = predict(nlsfit)))
```

## High Price Data Set
```{r}
ggplot(data, aes(Carat, Price)) + 
    geom_point() +
    coord_cartesian(xlim = c(0.7, 1.7), ylim = c(1800, 3250)) +
    geom_line(aes(y = predict(nlsfit)))
```



